\begin{flushright}
\textbf{5130201/40002, Semenov Ilya}
\par
\textbf{Active Vocabulary: 19, Grammar Structures: 6, Linkers: 19. Total: 595 words.}
\end{flushright}

\begin{center}
\textbf{Monologue on \textit{TRENDS}}
\end{center}

\noindent\small
\begin{longtable}{|p{0.25\textwidth}|p{0.5\textwidth}|p{0.2\textwidth}|}
\hline
\textbf{\textit{You are going to give a talk about TRENDS.}} & \textbf{The text of the monologue} & \textbf{Vocabulary, Grammar Structures, Linking Words and Phrases} \\
\hline

\textbf{Step 1. Introduction (94)}

1. Start with a hook sentence that will attract the listener's attention (a quote, a proverb, etc.).

2. Lead your speech steadily to the main part of your talk.

3. The introduction may consist of 3-6 sentences.
&
\textbf{1.} \hlcyan{As mentioned in a recent New Language Leader paragraph, ``these days it can be a problem keeping up with the number of new trends.''} This quote clearly shows how fast our world is changing. \hlcyan{In fact, if people want to stay up to date, they need to adapt quickly to new ideas and technologies.} \hllime{Moreover}, trends \hlcyan{are influenced} not only by fashion or music, \hllime{but also} by our habits and communication. \hllime{What is more}, understanding why some trends become global while others disappear \hlcyan{can} help us see how society develops in the digital age.
&
As mentioned in a recent New Language Leader paragraph, ``these days it can be a problem keeping up with the number of new trends.'';

if people want to stay up to date, they need to adapt quickly to new ideas and technologies;

are influenced;

can;

In fact;

but also;

What is more; \\
\hline

\textbf{Step 2. It's the New Thing (328)}

2.1. What is a trend? Speak about the way trends develop and people who are influential in their development.

2.2. Explain why trends might be important to business owners.
&
\textbf{2.1.} A trend is an idea, product or behaviour that \hlyellow{moves rapidly through a population} and often becomes \hlyellow{an overnight sensation}. \hllime{To begin with}, trends usually start when someone introduces something innovative or unusual that easily \hlyellow{grabs the headlines} and catches people's attention. \hllime{For example}, the growing trend of using artificial intelligence in everyday life has quickly \hlyellow{had a revival} as more and more people and companies begin to rely on it. Influencers and tech enthusiasts play a key role in its development because they are often the first \hlyellow{to tap into a trend} and promote it through \hlyellow{viral marketing campaigns}. \hllime{As a consequence}, AI tools have encouraged millions of users to do similar things and use the same types of technology in their daily routines. \hllime{Besides}, those who join such trends early \hlyellow{can be one step ahead of their competitors} and even \hlyellow{gain sales} by offering innovative products.

\vspace{0.5cm}

\textbf{2.2.} Trends \hllime{also} are very important to business owners because they show what people are interested in and how their behaviour is changing. \hllime{For instance}, the trend of using artificial intelligence helps companies \hlyellow{to understand the spending power} of their customers and create more personalised products. \hllime{Furthermore}, businesses that follow modern trends often manage to grow rapidly and attract new audiences. \hllime{In conclusion}, being aware of trends allows business owners \hlyellow{to have the same lifestyle and possessions} as their target customers and build stronger connections with them.
&
moves rapidly through a population;

an overnight sensation;

grabs the headlines;

had a revival;

to tap into a trend;

viral marketing campaigns;

be one step ahead of their competitors;

gain sales;

to understand the spending power;

to have the same lifestyle and possessions;

To begin with;

For example;

As a consequence;

Besides;

Also;

For instance;

Furthermore;

In conclusion \\
\hline

\textbf{Step 3. Describing a trend (510)}

3.1. Speak about current trends in different areas (e.g. education, work, music industry, etc.) that young people follow.

3.2. Choose one of the trends you have mentioned in 3.1 and describe major changes caused by the trend.
&
\textbf{3.1.} \hllime{As mentioned before}, the trend of using artificial intelligence continues \hlyellow{to show an upward trend}, especially in education and work. The number of people using AI tools has \hlyellow{risen by} over 60\% in the last two years. \hllime{In contrast}, traditional studying methods \hlyellow{remain steady}. Another current trend among young people is remote work, which became \hlyellow{twice as popular as it was before the pandemic}. In the music industry, digital platforms such us Yandex Music and Spotify have also \hlyellow{reached a peak} in popularity. \hllime{Overall}, these examples show that modern trends are shaping the way young people study, work and enjoy culture.

\vspace{0.5cm}

\textbf{3.2.} \hllime{Nowadays}, AI tools \hllime{such as} chatbots and virtual tutors \hlyellow{are becoming a must-have item} for students who want to learn more effectively. \hllime{At the same time}, many companies use AI \hlyellow{to be aware of social and cultural movements}. \hllime{As a result}, the demand for AI specialists \hlyellow{has doubled} in the last few years. \hllime{What is more}, this trend \hlyellow{is expected to have a lasting influence} on education and employment. \hllime{All in all}, AI has become an essential part of modern life.
&
to show an upward trend;

risen by;

remain steady;

twice as popular as it was before the pandemic;

reached a peak;

are becoming a must-have item;

to be aware of social and cultural movements;

has doubled;

to have a lasting influence;

As mentioned before;

In contrast;

Nowadays;

such as;

At the same time;

As a result;

What is more;

All in all;

is expected \\
\hline

\textbf{Step 4. CREATIVE THINKING}

Introduce your own extra idea(s) on trends that hasn't/haven't been mentioned before. Justify your choice.
&
One new trend is eco-friendly technology. More people choose sustainable products to protect the planet. This idea is becoming more popular every year and may \hlyellow{have a lasting influence} on future lifestyles. I believe it shows how environmental awareness \hlcyan{can} change the way we live and work.
&
have a lasting influence;

can \\
\hline

\textbf{Step 5. Conclusion}

Summarise the ideas of steps 2,3,4.
&
\hllime{To sum up}, trends influence our daily lives and decisions. AI and eco-friendly technology show how innovation transforms society. \hllime{Overall}, trends help people adapt to a changing world.
&
To sum up;

Overall \\
\hline
\end{longtable}
